Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-07 ms/main.tex
Fix figure S2

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

% Fluctuations in spatial model
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.75]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf}~\\
   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in a structured population.}
    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
    Both phenotypes start at 50\% frequency.
    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
    }
    %TODO: revisit this caption.
    \label{fig:spatial_fluctuations}
  \end{figure}

@@

%%% Figure: coexistence map
\begin{figure}[p]
  \centering
    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  \textbf{(a)} There is no oblique transmission, $v=1$.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  \textbf{(b)} Oblique transmission exists. 
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_recursive}
  \end{figure}

>>>>

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.56]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf} \\
    ~
    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

% Fluctuations in spatial model
%\begin{figure}[p]
%  \centering
%   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
%   \caption{
%    \textbf{Stable coexistence of both phenotypes in a structured population.}
%    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
%    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
%    Both phenotypes start at 50\% frequency.
%    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
%    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
%    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
%    }
%    %TODO: revisit this caption.
%    \label{fig:spatial_fluctuations}
%  \end{figure}

@@

%%% Figure: coexistence map
\begin{figure}[p]
  \centering
    \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
    \includegraphics[scale=0.4]{coexistence_with_oblique.eps}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
  The curves show the diffrence of $\hat{p}'-\hat{p}$ vs $\hat{p}$ where $\hat{p}'$ abd $\hat{p}$ are the frequency of the cooperative phenotype $A$ among juveniles in the next generation and current generations (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'-\hat{p}=0$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (red circle).
  When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
  \textbf{(a)} There is no oblique transmission, $v=1$.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  \textbf{(b)} Oblique transmission exists. 
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_recursive}
  \end{figure}
